---
title: "CS 422"
author: "Thupten Wangpo"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
  html_document:
    toc: yes
    df_print: paged
---

<!-- More information in R Markdown can be found at:
1. https://www.ssc.wisc.edu/sscc/pubs/RFR/RFR_RMarkdown.html  This is 
   the place to start since it is a short tutorial.
2. https://rmarkdown.rstudio.com/index.html This contains a longer 
   tutorial.  Take a look at the cheatsheet in 
   https://rmarkdown.rstudio.com/lesson-15.html, it is a concise 
   reference of R Markdown on two pages.
<-->

## Use this as a template for your homeworks.
#### Rename it to firstname-lastname.Rmd.
#### Run all the chunks by clicking on "Run" at the top right of the edit 
#### window and choose "Run All".  Assuming there were no errors in the
#### chunk, you should see a "Preview" button become visible on the top
#### left of the edit window.  Click this button and a html document should
#### pop up with the output from this R markdown script.


### Part 2.1
```{r}
# In the first chunk, set your working directory here and do other global 
# tasks like loading libraries.  See  
# https://bookdown.org/yihui/rmarkdown-cookbook/working-directory.html for
# more information.
knitr::opts_knit$set(root.dir = '/tmp')

FlightsDelayed <- read.csv("/Users/thupten/Desktop/CS422 Assignments/Thupten-Wangpo-HW2/DelayedFlights-Small.csv")
colSums(is.na(FlightsDelayed), na.rm = FALSE)
"There are 12 columns with NA in them"


```
### Part 2.2.

```{r}
"I think that weather causes the most travel woes. I think that Carrier causees the least delays"
delays <- FlightsDelayed[, c("CarrierDelay", "WeatherDelay", "NASDelay", "SecurityDelay", "LateAircraftDelay")]
delays
sum(delays$CarrierDelay)
```
### Part 1-C (Summary)
```{r}
# Add code here.  See manual page for the summary() command.
```

### Part 1-D
```{r}
# Add code here.  Save maximum speed in a variable called "max.speed" and
# minimum distance in a variable called "min.dist".  The code below will
# then print your output.

str <- paste0("Maximum speed is ", max.speed, ", and minimum distance is ", 
              min.dist)
str
```
### Part 1-E
```{r}
# Add code here
```

### Part 1-F
```{r}
# Add code here
```
